Deep ordinal classification based on cumulative link models

### 2019-05-24 paper/ieee.tex
Paper + fixed multiprocessing issue

\usepackage{hyperref}

@@

	\section{Introduction}
	\label{sect:introduction}
	% The very first letter is a 2 line initial drop letter followed
	% by the rest of the first word in caps.
	% 
	% form to use if the first word consists of a single letter:
	% \IEEEPARstart{A}{demo} file is ....
	% 
	% form to use if you need the single drop letter followed by
	% normal text (unknown if ever used by the IEEE):
	% \IEEEPARstart{A}{}demo file is ....
	% 
	% Some journals put the first two words in caps:
	% \IEEEPARstart{T}{his demo} file is ....
	% 
	% Here we have the typical use of a "T" for an initial drop letter
	% and "HIS" in caps to complete the first word.
	\IEEEPARstart{D}{eep learning}, introduced by Yann Lecun~\cite{lecun2015deep}, combines multiple machine learning techniques and allows computational models that are composed of numerous processing layers to learn representations of data with various levels of abstraction. These methods have dramatically improved the state-of-the-art in many domains, such as image classification~\cite{cirecsan2012multi,he2016deep,krizhevsky2012imagenet}, speech recognition~\cite{hinton2012deep}, control problems~\cite{mnih2015human}, object detection~\cite{jiang2016speed,girshick2014rich}, privacy protection~\cite{yu2017iprivacy}, recovery of human pose~\cite{hong2015multimodal}, semantic segmentation~\cite{long2015fully} and image retrieval~\cite{li2015weakly}. Convolutional Neural Networks (CNN) are one of the types of deep networks that are designed to process data that come in the form of multiple arrays. CNNs are appropriate for images, video, speech and audio processing, and they have been used extensively in the last years for automatic classification tasks~\cite{dong2014learning,sun2013deep,ronneberger2015u}. For images, each colour channel is represented by a 2D array, and convolutional layers extract the main features from the pixels, and, after that, a fully connected layer classify every sample based on its extracted features. At the output of the CNN, a softmax function provides the probabilities of the set of classes predefined in the model for classification tasks. However, the softmax may not be the best option depending on the problem considered.

@@

	In this paper, the probabilistic structure of CLMs is proposed as a link function for deep convolutional neural networks. This can be achieved by defining a new type of output layer alternative to the standard softmax layer. In this way, the proposed output layer will transform the one-dimensional projection, previously denoted as $f(\mathbf{x})$, into a set of probabilities. $f(\mathbf{x})$ is estimated from a nonlinear transformation of the set of features learnt by the previous layers, $l(\mathbf{x})=f(\mathbf{x})$, where $\mathbf{x}$ is the pattern being evaluated and $l(\mathbf{x})$ is a latent representation of the pattern given by the output of a single neuron. In order to apply unconstrained optimizers while ensuring $b_1 \le b_2 \le ... \le b_{Q-1}$, we can redefine the thresholds. All of them can be derived from the first one in the following form:
	\begin{equation}
	b_q = b_1 + \sum_{q=1}^{q-1} \alpha_q^2, \quad q = 2, ..., Q,
	\end{equation}
	where $b_1$ and $\alpha_q$ are the learnable parameters, and $Q$ is the number of classes.

@@

	\subsection{Model}
	\label{sect:model}
	CNNs have been used for both datasets. The different architectures of CNNs used in these experiments are presented in Tables \ref{table:CNNArchitecture} and \ref{table:ResNetArchitecture}. The architecture for DR is the same that was used in \cite{de2018weighted} and the network for Adience is a small Residual Network (ResNet) \cite{he2016deep} that was used in \cite{beckham2017unimodal}. The most important parameters for convolutional layers are the number of filters that are used to make the convolution operation, the size of these filters and the stride, which is the number of pixels that the filter is moved in every operation. Pooling layers have similar parameters: pool size (number of pixels that will be involved in the operation) and stride. For convolutional layers, ConvWxH@FsS stands for filters of size WxH and stride S. For pooling layers, PoolWxHsS corresponds to a pool size of WxH and stride S.

@@

	\begin{table}[!t]
		\caption{Description of the architecture used in the DR experiments.}
		\label{table:CNNArchitecture}
		\centering
		\begin{tabular}{lc}
			\hline
			\hline
			\textbf{Layer} & \textbf{Output shape}\\
			\hline
			%Conv3x3@32s1 & 254x254x32\\\hline
			2 x Conv3x3@32s1 & 252x252x32\\
			MaxPool2x2s2 & 126x126x32\\

			%Conv3x3@64s1 & 124x124x64\\\hline
			2 x Conv3x3@64s1 & 122x122x64\\
			MaxPool2x2s2 & 61x61x64\\

			%Conv3x3@128s1 & 59x59x128\\\hline
			2 x Conv3x3@128s1 & 57x57x128\\
			MaxPool2x2s2 & 28x28x128\\

			%Conv3x3@128s1 & 26x26x128\\\hline
			2 x Conv3x3@128s1 & 24x24x128\\
			MaxPool2x2s2 & 12x12x128\\

			Conv4x4@128s1 & 9x9x128\\
			\hline
			\hline
		\end{tabular}	
	\end{table}

	\begin{table}[!t]
		\caption{Description of the architecture used in the Adience experiments.}
		\label{table:ResNetArchitecture}
		\centering
		\begin{tabular}{lc}
			\hline
			\hline
			\textbf{Layer} & \textbf{Output shape}\\
			\hline
			Conv7x7@32s2 & 112x112x32\\
			MaxPool3x3s2 & 55x55x32\\
			2 x ResBlock3x3@64s1 & 55x55x32\\
			1 x ResBlock3x3@128s2 & 28x28x64\\
			2 x ResBlock3x3@128s1 & 28x28x64\\
			1 x ResBlock3x3@256s2 & 14x14x128\\
			2 x ResBlock3x3@256s1 & 14x14x128\\
			1 x ResBlock3x3@512s2 & 7x7x256\\
			2 x ResBlock3x3@512s1 & 7x7x256\\
			AveragePool7x7s2 & 1x1x256\\
			\hline
			\hline
		\end{tabular}	
	\end{table}

@@

	Fig. \ref{fig:lrdecay} represents the learning rate decay across $100$ epochs for the different initial values considered in this work.
	\begin{figure}[!t]
		\centering
		\includegraphics[width=3in]{img/lr.pdf}
		\caption{Representation of the learning rate decay.}
		\label{fig:lrdecay}
	\end{figure}

@@

	The test variable will be QWK, given by Eq. \eqref{eq:qwk}. We denote by $\text{QWK}_{i,j,k,l}(i,j,k\in \{1, 2, 3\})$ the value observed when the first factor is at the $i$-th level, the second at the $j$-th level and the third at the $k$-th level. We assume that the three factors do not act independently, and, therefore, there exists an interaction between each pair of them and between the three factors. In this case, the observations fit:
	\begin{equation}
	\nonumber
	\begin{aligned}
	\footnotesize
	\text{QWK}_{i,j,k,l} = \mu & + L_i + P_j + B_k + LP_{i,j} + LB_{i,k} \\& + PB_{j,k} + LPB_{i,j,k} + \epsilon_{i,j,k,l},
	\label{eq:anova3}
	\end{aligned}
	\end{equation}
	where $\mu$ is the fixed effect that is common to all the populations; $L_i$ is the effect associated with the \textit{i-th} level of the LF factor (\texttt{logit}, \texttt{probit}, \texttt{clog-log}); $P_j$ is the effect associated with the \textit{j-th} level of the LR factor and $B_k$ is the effect associated with the \textit{k-th} level of the BS factor. The term $LP_{i,j}$ denotes the joint effect of the presence of level $i$ of the first factor and level $j$ of the second one; this, therefore, is denominated the interaction term between $L$ and $P$ factors. The same interaction effect is appreciated on $LB_{i,k}$, $PB_{j,k}$ and $LPB_{i,j,k}$. The term $\epsilon_{i,j,k,l}$ is the influence on the results of everything that could not be evaluated or of random factors.

	We consider the null hypothesis that each term of the above equation is independent of the levels involved. The hypotheses for the levels of the L factor are $H_0 \equiv \left( L_1 = L_2 = L_3 \right),$ and $H_1 \equiv \left( \exists i,j | L_i\neq L_j\right)$. The same hypotheses are made for the other factors. 	The hypothesis associated with the interaction between $L$ and $P$ is $H_0 \equiv \left(LP_{i,j} = 0, \forall i,j\right)$, and $H_1 \equiv \left(\exists LP_{i,j} \ne 0\right)$. Similar hypotheses can be assumed for the interaction between the other factors.

	The ANOVA table represents the study in a compact form, containing the sum of squares, degrees of freedom, mean square value, test statistics and significance levels, where non-significative factors and interactions have been removed ($\text{p-value} > 0.05$). These factors and interactions take part on the error component. In this way, the results of the ANOVA III test for the DR dataset are summarised in Table  \ref{table:ANOVARetinopathy}. There are significant differences in average QWK depending on the LF and also depending on the LR for $\alpha=0.05$ ($\text{p-value} = 0.000$). Moreover, an interaction between the LF and the LR can be recognised ($\text{p-value} = 0.001$).

	\begin{table}[!t]
		\caption{ANOVA III for the analysis of the main factors in the design of a Convolutional Ordinal Neural Network for the Retinopathy dataset.}
		\label{table:ANOVARetinopathy}
		\centering
		\small
		\begin{tabular}{lccccc}
			\hline
			\hline
			           \multicolumn{6}{c}{Response variable QWK}             \\ \hline
			Source       &   S.S.   & D.F.  &  M.S.   &  F-ratio   &  Sig.   \\ \hline
			Model        & $37.860$ &  $9$  & $4.207$ & $1562.840$ & $0.000$ \\
			$L$ factor   & $0.057$  &  $2$  & $0.029$ &  $10.646$  & $0.000$ \\
			$P$ factor   & $0.121$  &  $2$  & $0.060$ &  $22.468$  & $0.000$ \\
			$LP$ factors & $0.057$  &  $4$  & $0.014$ &  $5.261$   & $0.001$ \\
			Error        & $0.339$  & $126$ & $0.003$ &            &  \\ \hline
			Total        & $38.199$ & $135$ &         &            & \\
			\hline
			\hline
		\end{tabular}
	\end{table}

	Given that there exist significant differences between the means, we analyse now these differences. A post-hoc multiple comparison test has been performed on the mean QWK obtained. An HSD Tukey's test \cite{tukey1949comparing} has been selected under the null hypothesis that the variance of the error of the dependent variable is the same between the groups. The results of this test over the test set are shown in Table \ref{table:TukeyDR}. They show that the best LF is the \texttt{clog-log} but the \texttt{probit} link performance is close to it. Also, the best value for the LR parameter is $10^{-3}$. The BS is not relevant for this dataset with the values considered.

	\begin{table}[!t]
		\caption{Tukey's test results for the DR dataset.}
		\label{table:TukeyDR}
		\centering
		\begin{tabular}{cccc}
			\hline\hline
			       LF         &        LF         & Mean diff. &  Sig.   \\ \hline
			 \texttt{logit}   &  \texttt{probit}  &  $-0.002$  & $0.011$ \\
			                  & \texttt{clog-log} &  $0.012$   & $0.000$ \\
			 \texttt{probit}  &  \texttt{logit}   &  $0.002$   & $0.011$ \\
			                  & \texttt{clog-log} &  $0.014$   & $0.248$ \\
			\texttt{clog-log} &  \texttt{logit}   &  $-0.012$  & $0.000$ \\
			                  &  \texttt{probit}  &  $-0.014$  & $0.248$ \\ \hline\hline
			       LR         &        LR         & Mean diff. &  Sig.   \\ \hline
			    $10^{-2}$     &     $10^{-3}$     &  $-0.073$  & $0.000$ \\
			                  &     $10^{-4}$     &  $-0.044$  & $0.000$ \\
			    $10^{-3}$     &     $10^{-2}$     &  $0.073$   & $0.000$ \\
			                  &     $10^{-4}$     &  $0.029$   & $0.023$ \\
			    $10^{-4}$     &     $10^{-2}$     &  $0.044$   & $0.000$ \\
			                  &     $10^{-3}$     &  $-0.029$  & $0.023$ \\ \hline\hline
		\end{tabular}
	\end{table}

	\begin{table}[!t]
		\caption{ANOVA III for the analysis of the main factors in the design of a Convolutional Ordinal Neural Network for the Adience dataset.}
		\label{table:ANOVAAdience}
		\centering
		\small
		\begin{tabular}{lccccc}
			\hline\hline
			            \multicolumn{6}{c}{Response variable QWK}             \\ \hline
			Source        &   S.S.   & D.F.  &  M.S.   &  F-ratio   &  Sig.   \\ \hline
			Model         & $84.372$ & $27$  & $3.125$ & $4414.006$ & $0.000$ \\
			$L$ factor    & $0.156$  &  $2$  & $0.078$ & $110.103$  & $0.000$ \\
			$P$ factor    & $0.925$  &  $2$  & $0.462$ & $653.163$  & $0.000$ \\
			$B$ factor    & $0.040$  &  $2$  & $0.020$ &  $28.218$  & $0.000$ \\
			$LP$ factors  & $0.284$  &  $4$  & $0.071$ & $100.118$  & $0.000$ \\
			$LB$ factors  & $0.008$  &  $4$  & $0.002$ &  $2.837$   & $0.028$ \\
			$PB$ factors  & $0.026$  &  $4$  & $0.007$ &  $9.267$   & $0.000$ \\
			$LPB$ factors & $0.021$  &  $8$  & $0.003$ &  $3.728$   & $0.001$ \\
			Error         & $0.076$  & $108$ & $0.001$ &            &  \\ \hline
			Total         & $84.449$ & $135$ &         &            &  \\ \hline\hline
		\end{tabular}
	\end{table}

	The results of the ANOVA III test for the Adience dataset are shown in Table \ref{table:ANOVAAdience}. First, we observe that there exist significant differences in average QWK concerning the three factors ($\text{p-value} = 0.000$). Secondly, we found interactions between all the pairs of factors and between all the three factors together (p-values $0.000$, $0.000$, $0.000$ and $0.001$, respectively).

	As we did for the DR dataset, a post-hoc multiple comparison test has been performed on the average QWK obtained for Adience. Under the null hypothesis that the variance of the error of the dependent variable is the same between the groups, the HSD Tukey's test has been applied. The results of this test over the test set are shown in Table \ref{table:TukeyAdience}.

	\begin{table}[!t]
		\caption{Tukey's test results for the Adience dataset.}
		\label{table:TukeyAdience}
		\centering
		\begin{tabular}{cccc}
			\hline\hline
			       LF         &        LF         & Mean diff. &  Sig.   \\ \hline
			 \texttt{logit}   &  \texttt{probit}  &  $0.046$   & $0.000$ \\
			                  & \texttt{clog-log} &  $0.084$   & $0.000$ \\
			 \texttt{probit}  &  \texttt{logit}   &  $-0.046$  & $0.000$ \\
			                  & \texttt{clog-log} &  $0.038$   & $0.000$ \\
			\texttt{clog-log} &  \texttt{logit}   &  $-0.084$  & $0.000$ \\
			                  &  \texttt{probit}  &  $-0.038$  & $0.000$ \\ \hline\hline
			       LR         &        LR         & Mean diff. &  Sig.   \\ \hline
			    $10^{-2}$     &     $10^{-3}$     &  $-0.046$  & $0.000$ \\
			                  &     $10^{-4}$     &  $0.148$   & $0.000$ \\
			    $10^{-3}$     &     $10^{-2}$     &  $0.046$   & $0.000$ \\
			                  &     $10^{-4}$     &  $0.194$   & $0.000$ \\
			    $10^{-4}$     &     $10^{-2}$     &  $-0.148$  & $0.000$ \\
			                  &     $10^{-3}$     &  $-0.194$  & $0.000$ \\ \hline\hline
			       BS         &        BS         & Mean diff. &  Sig.   \\ \hline
			       64         &        128        &  $-0.041$  & $0.026$ \\
			                  &        256        &  $-0.027$  & $0.000$ \\
			       128        &        64         &  $0.041$   & $0.026$ \\
			                  &        256        &  $0.014$   & $0.000$ \\
			       256        &        64         &  $0.027$   & $0.000$ \\
			                  &        128        &  $-0.014$  & $0.000$ \\ \hline\hline
		\end{tabular}
	\end{table}

>>>>

\usepackage[bookmarks=false]{hyperref}

@@

	\section{Introduction}
	\label{sect:introduction}
	% The very first letter is a 2 line initial drop letter followed
	% by the rest of the first word in caps.
	% 
	% form to use if the first word consists of a single letter:
	% \IEEEPARstart{A}{demo} file is ....
	% 
	% form to use if you need the single drop letter followed by
	% normal text (unknown if ever used by the IEEE):
	% \IEEEPARstart{A}{}demo file is ....
	% 
	% Some journals put the first two words in caps:
	% \IEEEPARstart{T}{his demo} file is ....
	% 
	% Here we have the typical use of a "T" for an initial drop letter
	% and "HIS" in caps to complete the first word.
	\IEEEPARstart{D}{eep learning}, introduced by Yann Lecun~\cite{lecun2015deep}, combines multiple machine learning techniques and allows computational models that are composed of numerous processing layers to learn representations of data with various levels of abstraction. These methods have dramatically improved the state-of-the-art in many domains, such as image classification~\cite{cirecsan2012multi,he2016deep,krizhevsky2012imagenet}, speech recognition~\cite{hinton2012deep}, control problems~\cite{mnih2015human}, object detection~\cite{jiang2016speed,girshick2014rich}, privacy and security protection~\cite{yu2017iprivacy,yuan2019adversarial,tan2018deep}, recovery of human pose~\cite{hong2015multimodal}, semantic segmentation~\cite{long2015fully} and image retrieval~\cite{li2015weakly}. Convolutional Neural Networks (CNN) are one of the types of deep networks that are designed to process data that come in the form of multiple arrays. CNNs are appropriate for images, video, speech and audio processing, and they have been used extensively in the last years for automatic classification tasks~\cite{dong2014learning,sun2013deep,ronneberger2015u}. For images, each colour channel is represented by a 2D array, and convolutional layers extract the main features from the pixels, and, after that, a fully connected layer classify every sample based on its extracted features. At the output of the CNN, a softmax function provides the probabilities of the set of classes predefined in the model for classification tasks. However, the softmax may not be the best option depending on the problem considered.

@@

	In this paper, the probabilistic structure of CLMs is proposed as a link function for deep convolutional neural networks. This can be achieved by defining a new type of output layer alternative to the standard softmax layer. In this way, the proposed output layer will transform the one-dimensional projection, previously denoted as $f(\mathbf{x})$, into a set of probabilities. $f(\mathbf{x})$ is estimated from a nonlinear transformation of the set of features learnt by the previous layers, $l(\mathbf{x})=f(\mathbf{x})$, where $\mathbf{x}$ is the pattern being evaluated and $l(\mathbf{x})$ is a latent representation of the pattern given by the output of a single neuron. In order to apply unconstrained optimizers while ensuring $b_1 \le b_2 \le ... \le b_{Q-1}$, we can redefine the thresholds. All of them can be derived from the first one in the following form:
	\begin{equation}
	\nonumber
	b_q = b_1 + \sum_{q=1}^{q-1} \alpha_q^2, \quad q = 2, ..., Q,
	\end{equation}
	where $b_1$ and $\alpha_q$ are the learnable parameters, and $Q$ is the number of classes.

@@

	\subsection{Model}
	\label{sect:model}
	CNNs have been used for both datasets. The different architectures of CNNs used in these experiments are presented in Table \ref{table:Architecture}. The architecture for DR is the same that was used in \cite{de2018weighted} and the network for Adience is a small Residual Network (ResNet) \cite{he2016deep} that was used in \cite{beckham2017unimodal}. The most important parameters for convolutional layers are the number of filters that are used to make the convolution operation, the size of these filters and the stride, which is the number of pixels that the filter is moved in every operation. Pooling layers have similar parameters: pool size (number of pixels that will be involved in the operation) and stride. For convolutional layers, ConvWxH@FsS stands for filters of size WxH and stride S. For pooling layers, PoolWxHsS corresponds to a pool size of WxH and stride S.

@@

%	\begin{table}[!t]
%		\caption{Description of the architecture used in the DR experiments.}
%		\label{table:CNNArchitecture}
%		\centering
%		\begin{tabular}{lc}
%			\hline
%			\hline
%			\textbf{Layer} & \textbf{Output shape}\\
%			\hline
%			2 x Conv3x3@32s1 & 252x252x32\\
%			MaxPool2x2s2 & 126x126x32\\
%			2 x Conv3x3@64s1 & 122x122x64\\
%			MaxPool2x2s2 & 61x61x64\\
%			2 x Conv3x3@128s1 & 57x57x128\\
%			MaxPool2x2s2 & 28x28x128\\
%			2 x Conv3x3@128s1 & 24x24x128\\
%			MaxPool2x2s2 & 12x12x128\\		
%			Conv4x4@128s1 & 9x9x128\\
%			\hline
%			\hline
%		\end{tabular}	
%	\end{table}
%	
%	\begin{table}[!t]
%		\caption{Description of the architecture used in the Adience experiments.}
%		\label{table:ResNetArchitecture}
%		\centering
%		\begin{tabular}{lc}
%			\hline
%			\hline
%			\textbf{Layer} & \textbf{Output shape}\\
%			\hline
%			Conv7x7@32s2 & 112x112x32\\
%			MaxPool3x3s2 & 55x55x32\\
%			2 x ResBlock3x3@64s1 & 55x55x32\\
%			1 x ResBlock3x3@128s2 & 28x28x64\\
%			2 x ResBlock3x3@128s1 & 28x28x64\\
%			1 x ResBlock3x3@256s2 & 14x14x128\\
%			2 x ResBlock3x3@256s1 & 14x14x128\\
%			1 x ResBlock3x3@512s2 & 7x7x256\\
%			2 x ResBlock3x3@512s1 & 7x7x256\\
%			AveragePool7x7s2 & 1x1x256\\
%			\hline
%			\hline
%		\end{tabular}	
%	\end{table}

	\begin{table}[!t]
		\caption{Description of the architecture used for each dataset.}
		\label{table:Architecture}
		\centering
		\resizebox{\columnwidth}{!}{
		\begin{tabular}{lclc}
			\hline\hline
			\multicolumn{2}{c}{\textbf{Diabetic Retinopathy}} & \multicolumn{2}{c}{\textbf{Adience}}\\
			\hline
			\textbf{Layer}  & \textbf{Output} & \textbf{Layer}      & \textbf{Output} \\ \hline
			2 Conv3x3@32s1  &   252x252x32    & Conv7x7@32s2        &   112x112x32    \\
			MaxPool2x2s2    &   126x126x32    & MaxPool3x3s2        &    55x55x32     \\
			2 Conv3x3@64s1  &   122x122x64    & 2 ResBlock3x3@64s1  &    55x55x32     \\
			MaxPool2x2s2    &    61x61x64     & ResBlock3x3@128s2   &    28x28x64     \\
			2 Conv3x3@128s1 &    57x57x128    & 2 ResBlock3x3@128s1 &    28x28x64     \\
			MaxPool2x2s2    &    28x28x128    & 1 ResBlock3x3@256s2 &    14x14x128    \\
			2 Conv3x3@128s1 &    24x24x128    & 2 ResBlock3x3@256s1 &    14x14x128    \\
			MaxPool2x2s2    &   12x12x128\    & 1 ResBlock3x3@512s2 &     7x7x256     \\
			Conv4x4@128s1   &     9x9x128     & 2 ResBlock3x3@512s1 &     7x7x256     \\
			                &                 & AveragePool7x7s2    &     1x1x256     \\ \hline\hline
		\end{tabular}}	
	\end{table}

@@

%	Fig. \ref{fig:lrdecay} represents the learning rate decay across $100$ epochs for the different initial values considered in this work.
%	\begin{figure}[!t]
%		\centering
%		\includegraphics[width=3in]{img/lr.pdf}
%		\caption{Representation of the learning rate decay.}
%		\label{fig:lrdecay}
%	\end{figure}

@@

%	The test variable will be QWK, given by Eq. \eqref{eq:qwk}. We denote by $\text{QWK}_{i,j,k,l}(i,j,k\in \{1, 2, 3\})$ the value observed when the first factor is at the $i$-th level, the second at the $j$-th level and the third at the $k$-th level. We assume that the three factors do not act independently, and, therefore, there exists an interaction between each pair of them and between the three factors. In this case, the observations fit:
%	\begin{equation}
%	\nonumber
%	\begin{aligned}
%	\footnotesize
%	\text{QWK}_{i,j,k,l} = \mu & + L_i + P_j + B_k + LP_{i,j} + LB_{i,k} \\& + PB_{j,k} + LPB_{i,j,k} + \epsilon_{i,j,k,l},
%	\label{eq:anova3}
%	\end{aligned}
%	\end{equation}
%	where $\mu$ is the fixed effect that is common to all the populations; $L_i$ is the effect associated with the \textit{i-th} level of the LF factor (\texttt{logit}, \texttt{probit}, \texttt{clog-log}); $P_j$ is the effect associated with the \textit{j-th} level of the LR factor and $B_k$ is the effect associated with the \textit{k-th} level of the BS factor. The term $LP_{i,j}$ denotes the joint effect of the presence of level $i$ of the first factor and level $j$ of the second one; this, therefore, is denominated the interaction term between $L$ and $P$ factors. The same interaction effect is appreciated on $LB_{i,k}$, $PB_{j,k}$ and $LPB_{i,j,k}$. The term $\epsilon_{i,j,k,l}$ is the influence on the results of everything that could not be evaluated or of random factors.

	%	We consider the null hypothesis that each term of the above equation is independent of the levels involved. The hypotheses for the levels of the L factor are $H_0 \equiv \left( L_1 = L_2 = L_3 \right),$ and $H_1 \equiv \left( \exists i,j | L_i\neq L_j\right)$. The same hypotheses are made for the other factors. 	The hypothesis associated with the interaction between $L$ and $P$ is $H_0 \equiv \left(LP_{i,j} = 0, \forall i,j\right)$, and $H_1 \equiv \left(\exists LP_{i,j} \ne 0\right)$. Similar hypotheses can be assumed for the interaction between the other factors.

	%	The ANOVA table represents the study in a compact form, containing the sum of squares, degrees of freedom, mean square value, test statistics and significance levels, where non-significative factors and interactions have been removed ($\text{p-value} > 0.05$). These factors and interactions take part on the error component. In this way, the results of the ANOVA III test for the DR dataset are summarised in Table  \ref{table:ANOVARetinopathy}.
	The ANOVA test results show that there are significant differences in average QWK depending on the LF and also depending on the LR for $\alpha=0.05$ ($\text{p-value} = 0.000$). Moreover, an interaction between the LF and the LR can be recognised ($\text{p-value} = 0.001$).

%	\begin{table}[!t]
%		\caption{ANOVA III for the analysis of the main factors in the design of a Convolutional Ordinal Neural Network for the Retinopathy dataset.}
%		\label{table:ANOVARetinopathy}
%		\centering
%		\small
%		\begin{tabular}{lccccc}
%			\hline
%			\hline
%			           \multicolumn{6}{c}{Response variable QWK}             \\ \hline
%			Source       &   S.S.   & D.F.  &  M.S.   &  F-ratio   &  Sig.   \\ \hline
%			Model        & $37.860$ &  $9$  & $4.207$ & $1562.840$ & $0.000$ \\
%			$L$ factor   & $0.057$  &  $2$  & $0.029$ &  $10.646$  & $0.000$ \\
%			$P$ factor   & $0.121$  &  $2$  & $0.060$ &  $22.468$  & $0.000$ \\
%			$LP$ factors & $0.057$  &  $4$  & $0.014$ &  $5.261$   & $0.001$ \\
%			Error        & $0.339$  & $126$ & $0.003$ &            &  \\ \hline
%			Total        & $38.199$ & $135$ &         &            & \\
%			\hline
%			\hline
%		\end{tabular}
%	\end{table}

	Given that there exist significant differences between the means, we analyse now these differences. A post-hoc multiple comparison test has been performed on the mean QWK obtained. An HSD Tukey's test \cite{tukey1949comparing} has been selected under the null hypothesis that the variance of the error of the dependent variable is the same between the groups. The results of this test over the test set are shown in Table \ref{table:Tukey}. They show that the best LF is the \texttt{clog-log} but the \texttt{probit} link performance is close to it. Also, the best value for the LR parameter is $10^{-3}$. The BS is not relevant for this dataset with the values considered.
%		
%	\begin{table}[!t]
%		\caption{Tukey's test results for the DR dataset.}
%		\label{table:TukeyDR}
%		\centering
%		\begin{tabular}{cccc}
%			\hline\hline
%			       LF         &        LF         & Mean diff. &  Sig.   \\ \hline
%			 \texttt{logit}   &  \texttt{probit}  &  $-0.002$  & $0.011$ \\
%			                  & \texttt{clog-log} &  $0.012$   & $0.000$ \\
%			 \texttt{probit}  &  \texttt{logit}   &  $0.002$   & $0.011$ \\
%			                  & \texttt{clog-log} &  $0.014$   & $0.248$ \\
%			\texttt{clog-log} &  \texttt{logit}   &  $-0.012$  & $0.000$ \\
%			                  &  \texttt{probit}  &  $-0.014$  & $0.248$ \\ \hline\hline
%			       LR         &        LR         & Mean diff. &  Sig.   \\ \hline
%			    $10^{-2}$     &     $10^{-3}$     &  $-0.073$  & $0.000$ \\
%			                  &     $10^{-4}$     &  $-0.044$  & $0.000$ \\
%			    $10^{-3}$     &     $10^{-2}$     &  $0.073$   & $0.000$ \\
%			                  &     $10^{-4}$     &  $0.029$   & $0.023$ \\
%			    $10^{-4}$     &     $10^{-2}$     &  $0.044$   & $0.000$ \\
%			                  &     $10^{-3}$     &  $-0.029$  & $0.023$ \\ \hline\hline
%		\end{tabular}
%	\end{table}

%	\begin{table}[!t]
%		\caption{ANOVA III for the analysis of the main factors in the design of a Convolutional Ordinal Neural Network for the Adience dataset.}
%		\label{table:ANOVAAdience}
%		\centering
%		\small
%		\begin{tabular}{lccccc}
%			\hline\hline
%			            \multicolumn{6}{c}{Response variable QWK}             \\ \hline
%			Source        &   S.S.   & D.F.  &  M.S.   &  F-ratio   &  Sig.   \\ \hline
%			Model         & $84.372$ & $27$  & $3.125$ & $4414.006$ & $0.000$ \\
%			$L$ factor    & $0.156$  &  $2$  & $0.078$ & $110.103$  & $0.000$ \\
%			$P$ factor    & $0.925$  &  $2$  & $0.462$ & $653.163$  & $0.000$ \\
%			$B$ factor    & $0.040$  &  $2$  & $0.020$ &  $28.218$  & $0.000$ \\
%			$LP$ factors  & $0.284$  &  $4$  & $0.071$ & $100.118$  & $0.000$ \\
%			$LB$ factors  & $0.008$  &  $4$  & $0.002$ &  $2.837$   & $0.028$ \\
%			$PB$ factors  & $0.026$  &  $4$  & $0.007$ &  $9.267$   & $0.000$ \\
%			$LPB$ factors & $0.021$  &  $8$  & $0.003$ &  $3.728$   & $0.001$ \\
%			Error         & $0.076$  & $108$ & $0.001$ &            &  \\ \hline
%			Total         & $84.449$ & $135$ &         &            &  \\ \hline\hline
%		\end{tabular}
%	\end{table}
%	
	The results of the ANOVA III test for the Adience dataset, first, demonstrate that there exist significant differences in average QWK concerning the three factors ($\text{p-value} = 0.000$). Secondly, we found interactions between all the pairs of factors and between all the three factors together (p-values $0.000$, $0.000$, $0.000$ and $0.001$, respectively).

	As we did for the DR dataset, a post-hoc multiple comparison test has been performed on the average QWK obtained for Adience. Under the null hypothesis that the variance of the error of the dependent variable is the same between the groups, the HSD Tukey's test has been applied. The results of this test over the test set are shown in Table \ref{table:Tukey}.

%	\begin{table}[!t]
%		\caption{Tukey's test results for the Adience dataset.}
%		\label{table:TukeyAdience}
%		\centering
%		\begin{tabular}{cccc}
%			\hline\hline
%			       LF         &        LF         & Mean diff. &  Sig.   \\ \hline
%			 \texttt{logit}   &  \texttt{probit}  &  $0.046$   & $0.000$ \\
%			                  & \texttt{clog-log} &  $0.084$   & $0.000$ \\
%			 \texttt{probit}  &  \texttt{logit}   &  $-0.046$  & $0.000$ \\
%			                  & \texttt{clog-log} &  $0.038$   & $0.000$ \\
%			\texttt{clog-log} &  \texttt{logit}   &  $-0.084$  & $0.000$ \\
%			                  &  \texttt{probit}  &  $-0.038$  & $0.000$ \\ \hline\hline
%			       LR         &        LR         & Mean diff. &  Sig.   \\ \hline
%			    $10^{-2}$     &     $10^{-3}$     &  $-0.046$  & $0.000$ \\
%			                  &     $10^{-4}$     &  $0.148$   & $0.000$ \\
%			    $10^{-3}$     &     $10^{-2}$     &  $0.046$   & $0.000$ \\
%			                  &     $10^{-4}$     &  $0.194$   & $0.000$ \\
%			    $10^{-4}$     &     $10^{-2}$     &  $-0.148$  & $0.000$ \\
%			                  &     $10^{-3}$     &  $-0.194$  & $0.000$ \\ \hline\hline
%			       BS         &        BS         & Mean diff. &  Sig.   \\ \hline
%			       64         &        128        &  $-0.041$  & $0.026$ \\
%			                  &        256        &  $-0.027$  & $0.000$ \\
%			       128        &        64         &  $0.041$   & $0.026$ \\
%			                  &        256        &  $0.014$   & $0.000$ \\
%			       256        &        64         &  $0.027$   & $0.000$ \\
%			                  &        128        &  $-0.014$  & $0.000$ \\ \hline\hline
%		\end{tabular}
%	\end{table}
